Dynamics of innovation along foraged trajectories

### 2023-04-19 LaTeX/innovate.tex
SmallUpdate

The interpretation of this equation is the the orientation dynamics of the agent undergoes a diffusion but the overall trajectory has 
an intrinsic curvature (arising out of the boundary condition). Here $s$ is the arc-length which is
equivalent to $k$-step motion of the agent i.e. $s_k = k l = k v_o \delta t$. Similarly $j$ in the
equation is the $j$-th epoch of $k$-step trajectory of the agent.

>>>>

The interpretation of this equation is the the orientation dynamics of the agent undergoes a diffusion but the overall trajectory has 
an intrinsic curvature (arising out of the boundary condition). Here $s$ is the arc-length which is
equivalent to $k$-step motion of the agent i.e. $s_k = k l = k v_o \delta t$. Similarly $j$ in the
equation is the $j$-th epoch of $k$-step trajectory of the agent. The location of the agent is given by
$\partial_s \r(s,j) = \th_\theta(s, j) = \{ \cos \phi(s, j), \sin \phi(s, j) \} = \{ -\sin \theta(s, j), \cos \theta(s, j) \}$. Once we know $\phi(s, j)$
can evaluate the position, $\r(s, j)$ and the orientation $\theta(s, j)$. In this framework
the policy $\pi_{\rm int} (\r(s))$ for the $j$-th epoch gives the action $\phi(s)$ that moves the agent
along using the geometric constraint/equation $\r'(s) = \th_\theta(s)$.
\textbf{Don't need temporal/epochal dynamics}
